---
title: "Create Observational and Interventional experiments on Asia Network"
author: "Megha"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this file, we simulate obseravtional and interventional experiment from the synthetic network Asia from the bnlearn package. We conduct two experiment one generating asia_mut1 with one intervention amd asia_mut2 with two intervention. This is done in the same way to replicate the process of Sachs data generation. We also add unknown "fat-hand" intervention by changing values of one or more of the target node's children.

```{r include=FALSE, cache=FALSE}
#loading the packages
install.packages("bnlearn")
library(bnlearn)
source("http://bioconductor.org/biocLite.R")
biocLite("Rgraphviz")
library(Rgraphviz)
library(ggplot2)
source("https://bioconductor.org/biocLite.R")  ##Use to load gRain package since RBGL is removed from CRAN repository
biocLite("RBGL")
library(gRain) 
library(gRbase)
```

```{r}
# load the Asia dataset.
data(asia)
# create and plot the network structure.
dag_asia = model2network("[A][S][T|A][L|S][B|S][D|B:E][E|T:L][X|E]")
```

```{r}
#Sampling some observational data points from asia dataset
asia_mut1_obs = asia[sample(nrow(asia), 1600), ]

#intitializing additional column for Intervened target
Int_col = 0

#Adding the INT column
asia_mut1_obs$INT = Int_col
```

```{r}
#First we start by learning parameters of the Bayesian Network given the DAG
fitted = bn.fit(dag_asia, asia, method = "bayes")
```

Performing queries using gRain package on a mutilated Bayesian Network where we performed a perfect intervention by setting Lung cancer as "Yes". This is similar to a lab experiment where we intervene L like a knock-out experiment in the real world.

```{r}
#Adding perfect intervening at node "L" and fat-hand intervention at node "E"
asia_mut1_network = mutilated(fitted, evidence = list(L = "no", E = "yes"))
jmutilated = compile(as.grain(asia_mut1_network))

#Sampling experimental data
asia_mut1_exp = rbn(asia_mut1_network,400)

#Intitializing additional column for the known intervened target L
Int_col = 4

#Adding the INT column
asia_mut1_exp$INT = Int_col
```

```{r}
#Combining observation and experiment into one dataframe
asia_mut1 = rbind(asia_mut1_obs, asia_mut1_exp)
write.csv(asia_mut1,"data/Asia data/asia_mut1.csv",row.names=FALSE)
```


Simulating data for with one observational and two interventinal experiments.
```{r}
#Sampling some observational data points from asia dataset
asia_mut2_obs = asia[sample(nrow(asia), 1200), ]

#intitializing additional column for Intervened target
Int_col = 0

#Adding the INT column
asia_mut2_obs$INT = Int_col 
```

Performing queries using gRain package on a mutilated Bayesian Network where we performed a perfect intervention by setting Lung cancer as "Yes" and Tuberculosis as "Yes". 

```{r}
#Adding perfect intervening at node "L" and fat-hand intervention at node "E"
asia_mut2_network = mutilated(fitted, evidence = list(L = "no", E = "yes"))
jmutilated = compile(as.grain(asia_mut2_network))

#Sampling experimental data
asia_mut2_exp1 = rbn(asia_mut2_network,400)

#Intitializing additional column for the known intervened target L
Int_col = 4

#Adding the INT column
asia_mut2_exp1$INT = Int_col

#Adding perfect intervening at node "T"
asia_mut2_network = mutilated(fitted, evidence = list(T = "yes"))
jmutilated = compile(as.grain(asia_mut2_network))


#Sampling experimental data
asia_mut2_exp2 = rbn(asia_mut2_network,400)

#Intitializing additional column for the known intervened target L
Int_col = 3

#Adding the INT column
asia_mut2_exp2$INT = Int_col
```

```{r}
#Combining observation and experiment into one dataframe
asia_mut2 = rbind(asia_mut2_obs, asia_mut2_exp1, asia_mut2_exp2)
write.csv(asia_mut2,"data/Asia data/asia_mut2.csv",row.names=FALSE)
```
