---
title: "Create Observational and Interventional experiments on Cancer Network"
author: "Megha"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this file, we simulate obseravtional and interventional experiment from the synthetic network Asia from the bnlearn package. We conduct two experiment one generating asia_mut1 with one intervention amd asia_mut2 with two intervention. This is done in the same way to replicate the process of Sachs data generation. We also add unknown "fat-hand" intervention by changing values of one or more of the target node's children.

```{r include=FALSE, cache=FALSE}
#loading the packages
install.packages("bnlearn")
library(bnlearn)
source("http://bioconductor.org/biocLite.R")
biocLite("Rgraphviz")
library(Rgraphviz)
library(ggplot2)
source("https://bioconductor.org/biocLite.R")  ##Use to load gRain package since RBGL is removed from CRAN repository
biocLite("RBGL")
library(gRain) 
library(gRbase)
```

```{r}
#load the Cancer dataset
cancer <- readRDS("~/Work_Space/CausalAnalysis_with_KGprior/data/Cancer/cancer.rds")
# create and plot the network structure.
dag.cancer_groundtruth = model2network("[Pollution][Smoker][Cancer|Pollution:Smoker][Xray|Cancer][Dyspnoea|Cancer]")

```

```{r}
#Sampling some observational data points from asia dataset
cancer_mut_obs = rbn(cancer,1000)

#intitializing additional column for Intervened target
Int_col = 0

#Adding the INT column
cancer_mut_obs$INT = Int_col
```

```{r}
#First we start by learning parameters of the Bayesian Network given the DAG
fitted = cancer
```

Performing queries using gRain package on a mutilated Bayesian Network where we performed a perfect intervention by setting Lung cancer as "Yes". This is similar to a lab experiment where we intervene L like a knock-out experiment in the real world.

```{r}
#Adding perfect intervening at node "Smoker" 
cancer_mut_network = mutilated(fitted, evidence = list(Smoker = "True"))
jmutilated = compile(as.grain(cancer_mut_network))

#Sampling experimental data
cancer_mut_exp = rbn(cancer_mut_network,400)

#Intitializing additional column for the known intervened target L
Int_col = 2

#Adding the INT column
cancer_mut_exp$INT = Int_col
```

```{r}
#Combining observation and experiment into one dataframe
cancer_mut = rbind(cancer_mut_obs, cancer_mut_exp)
write.csv(cancer_mut,"/Users/megha/Work_Space/CausalAnalysis_with_KGprior/data/Cancer/cancer_mut.csv",row.names=FALSE)
```

